### 2021-04-27 input/figproofA.tex
mostly about implem
wip
wip rw up to broadcast

  \newcommand\X{95pt}
  \newcommand\Y{-50pt}

@@

  \draw[<->] (5pt - \X, 0.4*\Y) -- node[below, font=\small]{\textbf{I: propagation}} (-5pt, 0.4*\Y); %% I

@@

  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below, font=\scriptsize]{somewhere: $\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};

>>>>

  \newcommand\X{95pt}
  \newcommand\Y{-60pt}

@@

  \draw[<->] (5pt - \X, 0.4*\Y) -- node[below, font=\small, align=center]{\textbf{I: propagation}\\\textbf{of $\alpha$ messages}} (-5pt, 0.4*\Y); %% I

@@

  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below, font=\scriptsize]{some \process somewhere: $\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};

### 2021-04-27 input/related_work.tex
wip rw up to broadcast

\begin{asparadesc}
\item [Remote third-party:]
Relying on a remote third party service is a popular approach to offer content indexing in geo-distributed infrastructures. 
Such a remote service should
\begin{inparaenum}[(i)]
\item have access to the list of current replica locations and
\item be aware of the topology to decide which replica is the
  closest for a given location.
\end{inparaenum}

\begin{inparaenum}[(i)]
\item Numerous solutions~\cite{snamp, p2p-oracle, fogstore, p2p-alto} maintain an index of all replica
locations on a centralized server. This comes with well-known disadvantages
inherent to centralized solutions such as load balancing, robustness or locality that are even magnified in an Edge context.
Distributing this index among nodes in the network circumvent some of
these issues, either using coordinate-based overlays~\cite{voronet,
  coin_19} or \underline{D}istributed \underline{H}ash
\underline{T}ables (DHTs)~\cite{ipfs, mdht, squirrel}. In
the latter, each node stores a part of the index, defined by an
interval between hash values.  Before downloading any object, a node
first hashes the content to obtain the address of the node that stores
the replica locations of this given object. After obtaining from the
remote node the list of available replicas, it can select the closest
copy to download from. We emphasize that, in this setting, the DHT
only stores information about replicas locations, not the content
itself.

\item Determining where resides the closest replica necessarily involves some knowledge about the current topology.
Maintaining a consistent view of an ever changing
topology across a network is inherently complicated, especially in
asynchronous settings. As for the index,
this knowledge about the topology can be either
centralized~\cite{topology-discovery} or distributed like in routing
protocols such as \underline{O}pen \underline{S}hortest
\underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
\end{inparaenum}

All the aforementionned solutions require to contact a remote node to request this index which is costly in terms of
latency while in contradiction with Edge infrastructure constraints, as previously explained.

>>>>

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services host by possibly remote third-party \processes~\REF;
and cutting the middleman requires that each \process maintains its
own index in a decentralized fashion~\REF. This section reviews these
approaches.

\begin{asparadesc}
\item [Third-party:]

Dedicated services possibly hosted by remote third-party \processes
are popular, for they propose the simplest mean to deploy such
service. They must maintain
\begin{inparaenum}[(i)]
\item the list of current replicas along with their respective
  location; and
\item the network topology to determine the closest replica for every
  requesting \process.
\end{inparaenum}

\noindent A central server that registers both these
information~\cite{snamp, p2p-oracle, fogstore, p2p-alto} facilitates
the computation, for it gathers all knowledge in one place. However,
it comes with well-known issues inherent to its distribution paradigm
such as load balancing, or single point of failure.
%% Numerous solutions
%% maintain an index of all replica locations on a centralized
%% server. This comes with well-known disadvantages inherent to
%% centralized solutions such as load balancing, robustness or locality
%% that are even magnified in an Edge context.

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
locality issues where \processes
\begin{inparaenum}[(i)]
\item request to a possibly far away location service the content
  location, and then
\item request the actual content from far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between DHT
servers possibly distant from each others, the \node gets a list of
available replicas. Contrarily to \NAME, such services do not ensure
to include the closest replica.

\noindent In addition, they often do not include distance information
along with replica location. Determining where resides the closest
replica for every requesting \process necessarily involves some
knowledge about the \emph{current} topology.  Maintaining a consistent
view of an ever changing topology across a network is inherently
complicated~\cite{topology-discovery, ospf}.
%%  As for the index, this knowledge about the topology can be either
%% centralized~\cite{topology-discovery} or distributed like in
%% routing protocols such as \underline{O}pen \underline{S}hortest
%% \underline{P}ath \underline{F}irst (OSPF)~\cite{ospf}.
As consequence, the requesting \node ends up downloading from multiple
replica hosts, yet only keeping the fastest answer. \Processes either
waste network resources, or face lower response time.

% We emphasize that, in this setting, the DHT only stores information
% about replicas locations, not the content itself.

%% Distributing this index among \processes in the network circumvent
%% some of these issues, either using coordinate-based
%% overlays~\cite{voronet, coin_19} or \underline{D}istributed
%% \underline{H}ash \underline{T}ables (DHTs)~\cite{ipfs, mdht,
%%   squirrel}. In the latter, each node stores a part of the index,
%% defined by an interval between hash values.  Before downloading any
%% object, a node first hashes the content to obtain the address of the
%% node that stores the replica locations of this given object. After
%% obtaining from the remote node the list of available replicas, it can
%% select the closest copy to download from. We emphasize that, in this
%% setting, the DHT only stores information about replicas locations, not
%% the content itself.

%% \noindent All the aforementionned solutions require to contact a remote node to
%% request this index which is costly in terms of latency while in
%% contradiction with Edge infrastructure constraints, as previously
%% explained.
